Supporting Information : Impact of asymmetric tail-dependence in extreme climatic events on extinction risk in population ecology

### 2019-03-17 MainText.Rmd
methods written

<!--test hypothesis from Q2 : ext risk with density-dependence metapopulation model with r from different regime-->
To test our hypothesis from (Q2) of \nameref{intro} for each metapopulation model,
we estimated extinction risk for a wide range of parameter $r$ 
which covered the undercompensatory and overcompensatory regime. We 
chose equispaced values of $r$ from the 95\% quantiles 
of possible range ($r_{min},r_{bf}$), where $r_{min}$ was the minimum value of $r$ 
for which the model equilibrium $P_e$ had always a finite, positive initial 
population (for details, see Appendix \ref{SM-model_stability}). For each chosen $r$ of each 
model where metapopulation could disperse locally with varying dispersal 
rate $d= 0,0.1,0.2,..0.5$, we calculated extinction risk with left 
tail dependent and right tail dependent environmental noise 
in different simulations, respectively. We also repeated the analysis 
for global dispersal for each metapopulation model. Script 
[`mydispersal.R`](https://github.com/sghosh89/ERC/blob/master/mydispersal.R) was used for this 
analysis.

@@

>>>>

<!--test hypothesis from Q2 : ext risk with density-dependence metapopulation model with r from different regime-->
To test our hypothesis from (Q2) of \nameref{intro} for each metapopulation model,
we estimated extinction risk for a wide range of parameter $r$ 
which covered the undercompensatory and overcompensatory regime. We 
chose equispaced values of $r$ from the 95\% quantiles 
of possible range ($r_{min},r_{bf}$), where $r_{min}$ was the minimum value of $r$ 
for which the model equilibrium $P_e$ had always a finite, positive initial 
population (for details, see Appendix \ref{SM-model_stability}). For each chosen $r$ from each 
model where metapopulation could disperse locally with varying dispersal 
rate $d= 0,0.1,0.2,..0.5$, we calculated extinction risk with left 
tail dependent and right tail dependent environmental noise 
in different simulations, respectively. We also repeated the analysis 
for global dispersal for each metapopulation model. Script 
[`mydispersal.R`](https://github.com/sghosh89/ERC/blob/master/mydispersal.R) was used for this 
analysis.

@@

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{1pt}
\noindent

### 2019-03-17 SuppMat.Rmd
methods written

**Verhulst model**

**Austin-Brewer model**

# References

@@

>>>>

**Verhulst model** [@cohen1995unexpected; @may1976bifurcations] is a discrete time difference 
representation of logistic growth of non-human biological population and can be written 
as $P_{t+1} = F(P_t,r,K) =P_t[1+r(1-P_t/K)]$, wirh $r>0$ and $K>0$ being growth rate and carrying capacity, respectively. 
Model equilibrium $P_e=0$ is always unstable whereas $P_e=K$ is stable below Hopf-bifurcation 
point $r_{bf}(=2)$. Model at stable equilibrium ($P_e=K$) lies in the under-compensatory regime when $0<r<r_c$
and in over-compensatory regime when $rc<r<r_{bf}$ with $r_c$ being equal to 1.

**Austin-Brewer model** [@austin1971world; @cohen1995unexpected], unlike from the first
five models we considered,
is used to model growth of human population. It follows the
discrete dynamics : $P_{t+1} = F(P_t,r,K,s)= P_t[1+r(K-P_t) \left\{ 1-\exp (-sP_t)\right\}]$, where
$r, K, s$ are positive, representing growth rate, carrying capacity 
and model parameter, respectively.
Usual extinction equilibrium is $P_e=0$. The other
finite, positive equilibrium is $P_e=P^\star=1-rK\left\{ 1-\exp (-sK)\right\}$. The equilibrium $P^\star$
is stable when $r<r_{bf}$ and unstable beyond the bifurcatio point $r_{bf} = \frac{2}{K[1-\exp (-sK)]}$.
After perturbation, model can return back monotonically to its stable equilibrium if parameter $r$ lies in the 
under-compensatory regime ($0<r<r_c$), where $r_c = \frac{1}{K[1-\exp (-sK)]}$. In the 
over-compensatory regime ($r_c<r<r_{bf}$), model approaches to stable equilibrium $P^\star$
in oscillatory fashion.

@@

# References 
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{1pt}
\noindent
